InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-02-06 paper.tex
Remove sentence

@@

For the ease of use and low time consumption we implemented a simple python command line interface, that makes it easy to define a pipeline consisting of a generator, processor and evaluator. It is also possible to enter multiple processors for one pipeline to stack and apply them together on the content.

The resulting pipelines, especially for images, were very resource intensive and could not be run efficiently on our own machines. We chose to use the free Google Colab resources, consisting of a NVIDIA Tesla T4 GPU that speeds up the pipelines up to 40x compared to our local execution time and allowed us to use the same environment for all experiments.

>>>>

Another image generative model is \textbf{midjourney} \cite{midjourney}. This model was created by an identically named and independent research lab. It can synthesize images from textual descriptions. Midjourney tends to generate surrealistic images and is popular among artists. It uses modern deep learning methods to create high-quality images.

\textbf{Imagen} is a text-to-image diffusion model with an unprecedented degree of photorealism and a deep level of language understanding. Imagen builds on the power of large transformer language models in understanding text and hinges on the strength of diffusion models in high-fidelity image generation. \cite{imagen} \cite{saharia2022photorealistic}.

@@
